On Star Formation at Dynamical Resonances of the Bar

### 2020-07-10 paper/ms.tex
More updates to paper

\newcommand{\Msun}{\ensuremath{\text{M}_{\odot}}}

@@

\section{Introduction}
Roughly two-thirds of spiral galaxies are known to host bars in the
near-infrared, about half of which are strong
\citep[e.g.][]{2000AJ....119..536E}.

@@

\subsection{Initial Conditions}
The starting point for the construction of our initial conditions is the
N-body model GALAKOS \citep{2020ApJ...890..117D}. GALAKOS has structural
parameters and a circular velocity curve which are in reasonable agreement
with current data. However, GALAKOS is a particularly good starting point
because as \citet{2020ApJ...890..117D} showed, the disk forms a strong bar
after ~ 1 Gyr. The bar then grows, until at ~ 2.5 Gyr it has grown and slowed
down to a pattern speed of ~40 km/s/kpc. Evidence is mounting that the Milky
Way's bar is long and slow, just like that in GALAKOS.

@@

Our goal is now to construct an initial disk galaxy with gas that, like
GALAKOS, forms a strong bar. The underlying method GALAKOS uses (namely
MakeNewDisk) can already convert a fraction of the initial stellar disk to a
gas disk which is initially in hydrostatic equilibrium. However, if this setup
is naive

>>>>

\newcommand{\Msun}{\ensuremath{\text{M}_{\odot}}}
\newcommand{\K}{\ensuremath{\text{K}}}

@@

\section{Introduction}
Roughly two-thirds of spiral galaxies are known to host bars in the
near-infrared, about half of which are strong
\citep[e.g.][]{2000AJ....119..536E}. Given their ubiquity, it is no surprise
that the Milky Way is known to host a strong bar. A full understanding of the
origin of the Galaxy's structure clearly rests on the impact of the bar not
just in the inner region but also near the Solar circle. Its impact on the gas
phase is highly discussed in the inner regions of the Galaxy, but studies of
the bar's impact on star formation at the Solar circle are less developed. In
this work, we seek to contribute to our understanding of the latter topic.

@@

\subsection{Initial Conditions}\label{ssec:ics}
The starting point for the construction of our initial conditions is the
N-body model GALAKOS \citep{2020ApJ...890..117D}. GALAKOS has structural
parameters and a circular velocity curve which are in reasonable agreement
with current data. However, GALAKOS is a particularly good starting point
because as \citet{2020ApJ...890..117D} showed, the disk forms a strong bar
after ~ 1 Gyr. The bar then grows, until at ~ 2.5 Gyr it has grown and slowed
down to a pattern speed of ~40 km/s/kpc. Evidence is mounting that the Milky
Way's bar is long and slow, just like that in GALAKOS.

@@

\subsection{Gas Accretion}\label{ssec:gas_acc}
The method described in Section~\ref{ssec:ics} will succesfully form a bar
after a few Gyr. However, because the disk is isolated (i.e., the only gas
present in the initial conditions is in the disk), there is no source of fresh
gas to resupply the disk. We found in empirical tests that by the time the bar
had fully formed, the disk had become significantly more quiescent than what
is expected for the Milky Way, with a global SFR of <~0.5 Msun/yr and a SFR
surface density at 8 kpc about two orders of magnitude less than expected.
Such differences prohibit a faithful comparison to the Milky Way.

As a result, it is necessary to include a source of fresh gas to resupply the
galaxy. We found this to be quite problematic because several such techniques
we explored would either weaken or completely destroy the bar. We found that
it was necessary to include a somewhat \textit{ad hoc} implementation of gas
accretion from the circumgalactic medium (CGM).

Our method is inspired by the picture of a ``galactic fountain flow''
\citep{2006MNRAS.366..449F, 2008MNRAS.386..935F}. In this picture, gas is
launched from the central region of a spiral galaxy before falling back onto
the disk at a larger radii. In these models, the gas has lower angular
momentum than the disk when it rejoins the disk due to {\bf drag interactions
with the hot corona.}

We therefore have implemented a method to include ``hoses'' into AREPO. These
hoses are circular regions of radius $R_h$ placed along the $x$-axis at $x=\pm
R$. At a fixed timestep $\delta t$ each hose will spawn a number $N$ of gas
particles. The spawned gas particles have a fixed mass, a uniform initial
temperature of $10^4 \K$, and a uniform metallicity chosen to be solar.

\subsection{Summary}\label{ssec:ics_summary}

Our goal is now to construct an initial disk galaxy with gas that, like
GALAKOS, forms a strong bar. The underlying method GALAKOS uses (namely
MakeNewDisk) can already convert a constant fraction of the initial stellar disk to a
gas disk which is initially in hydrostatic equilibrium. However, if this setup
is used na
